%% vim:tw=66:spell:wrap:ft=tex:
\ifx \printpresenthandout \undefined
	\ifx \printpresentarticle \undefined
		% no handout and no article
		\documentclass{beamer}
	\else
		% print article
		\documentclass[11pt]{article}
		\usepackage{beamerarticle}
	\fi
\else
	% handout
	\documentclass[handout]{beamer}
\fi
% Preamble
\input{preamble/present-helper.tex}

\begin{document}
% {{{ Meta
% meta needs to be in \begin{document} so that tabular works
\input{meta/present.tex}
%% transitions are made transparent rather than hidden
\setbeamercovered{transparent}
%  - Title slide.%{{{
\frame{\titlepage}
%}}}

\section{Problem}
\begin{frame}\frametitle{\secname}
	\begin{description}
		\item[P0] You have Perl code that needs to run on
			Windows (e.g., user requirements,
			Windows-only software/hardware support).
		\pause
		\item[P1] It can't be done in pure-Perl.
		\pause
		\item[P2] It requires many tricky-to-install
			native dependencies.
	\end{description}
\end{frame}

\section{Terminology}
\begin{frame}\frametitle{\secname}
\begin{itemize}[<+->]
	\item \href{https://www.cygwin.com/}{Cygwin}: POSIX-like environment for Windows (uses
		\texttt{cygwin1.dll}).
	\item \href{http://mingw.org/}{MinGW}: GCC-based toolchain for Windows (32/64-bit)
	\item MSYS: part of the MinGW project; shell and utilities forked from Cygwin a long
		time ago (e.g., run \texttt{./configure}).
	\item \href{https://www.msys2.org/}{MSYS2}: project to combine MinGW with updates from
		Cygwin and a package manager.
	\item Other approaches: \href{https://docs.microsoft.com/windows/wsl}{Windows Subsystem for Linux}.
\end{itemize}
\end{frame}

\section{Who uses MSYS2}
\begin{frame}\frametitle{\secname}
\begin{itemize}
	\item \href{https://cran.r-project.org/bin/windows/Rtools/}{Rtools}
		(starting with R 4.0.0),
	\item \href{https://github.com/oneclick/rubyinstaller2}{RubyInstaller},
	\item \href{https://pygobject.readthedocs.io/en/latest/getting_started.html#windows-getting-started}{PyGObject},
	\ldots
	\item and several other FOSS projects recommend it
		as their build environment.
\end{itemize}
\end{frame}

\section{Installing All Your Base}
\defverbatim\pacmanInstallPerl{
\small
\begin{verbatim}
pacman -S mingw-w64-x86_64-perl mingw-w64-x86_64-toolchain
\end{verbatim}
}
\begin{frame}\frametitle{\secname}
\begin{itemize}
	\item Go to \url{https://www.msys2.org/} and follow the
		installation instructions (or use the
		\href{https://chocolatey.org/packages/msys2}{Chocolatey}
		to automate).
	\pause\item Open a terminal for one of the subsystems:
		\begin{description}
			\item[MSYS] For building code that
				requires the compatibility layer.
			\item[MINGW32] For 32-bit code.
			\item[MINGW64] For 64-bit code. This is
				most likely what you want.
		\end{description}
	\pause\item Install Perl for MINGW64 and the toolchain (for compiling XS)
		\pacmanInstallPerl
\end{itemize}
\end{frame}

\section{Install your packages\ldots for great justice.}
\defverbatim\pacmanSearch{
\small
\begin{verbatim}
pacman -Ss <query>
\end{verbatim}
}
\defverbatim\pacmanInstall{
\small
\begin{verbatim}
pacman -S mingw-w64-x86_64-gstreamer \
  mingw-w64-x86_64-gst-plugins-base \
  mingw-w64-x86_64-gst-plugins-good \
  mingw-w64-x86_64-gobject-introspection
\end{verbatim}
}
\begin{frame}\frametitle{\secname}
\begin{itemize}[<+->]
	\item Find your package by either browsing
		\url{https://github.com/msys2/MINGW-packages} or
		searching at the prompt:
		\pacmanSearch
	\items Examples: SDL2, FFTW, GStreamer.
	\item Install the packages
		\pacmanInstall
\end{itemize}
\end{frame}

\section{Further information}
\begin{frame}\frametitle{\secname}
	\begin{itemize}
		\item Steps on building \texttt{Gtk3.pm}
			\url{http://project-renard.github.io/doc/development/meeting-log/posts/2016/05/03/windows-build-with-msys2/}.
		\item Script that automates installation of
			\texttt{Gtk3.pm}: \url{https://github.com/MaxPerl/perl-Gtk3-windows-installer}.
	\end{itemize}
\end{frame}


\section{Questions / Contact}
\begin{frame}\frametitle{\secname}
Reach out
\begin{itemize}
	\item on IRC: \texttt{sivoais} on \url{irc://irc.perl.org/#native} (we can also chat
		about Alien and FFI!),
	\item on Twitter: \href{https://twitter.com/zmughal}{@zmughal},
	\item on GitHub: \url{https://github.com/zmughal}.
\end{itemize}
\end{frame}


%%% }}}
%%% {{{ END

% Blank frame
%\begin{frame}\frametitle{\secname}
%\end{frame}

\end{document}
